Measuring causal influence with\\ back-to-back regression: the linear case - supplementary material

### 2019-05-23 paper/meg_exps.tex
almost done fellas

The three types of analyses were implemented for each subject and each time
sample independently. To estimate the reliability of these estimates in the
population, we tested, using one-sample $t$-test whether the distribution of
the estimated contribution of each factor different from baseline ($t=0$ms),
as $\text{t-test}(\hat E_{t=0} - \hat E_{\tau})$, with $\tau \in $ ranging from
150ms to 1s after word onset. We use the resulting t and p-values as proxy to
quantify the performance of each model. These results are depicted in Figure
\ref{fig:meg_pval}. For concision purposes, we only report this metric averaged
between 150ms and 1s after word onset.

@@

Finally we investigate in Figure \ref{fig:megresult} whether B2B was sufficiently sensitive to reliably detect a multiplicity of subtle features, such as individual letters and part-of-speech. The vast majority the visual and lexical features appeared to be reliably detected \ref{fig:megbar}. B2B thus promises to improve the detectability of subtle effects.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_result.pdf}
  \caption{Cumulative estimates of word features as a function of time relative to word onset (chance level = 0). The dark blue area (word length) and dark red area (word frequency) correspond to the same data as those of the B2B average across subjects presented in \label{fig:meg_twocurves}. A variety of visual features peak around 150ms, while a variety of lexical features tend to peak around 400ms.}
  \label{fig:megresult}
\end{figure}

>>>>

The three types of analyses were implemented for each subject and each time
sample independently. To estimate the reliability of these estimates in the
population, we tested, using one-sample $t$-test whether the distribution of
the estimated contribution of each factor different from baseline ($t=0$ms),
as $\text{t-test}(\hat E_{t=0} - \hat E_{\tau})$, with $\tau \in $ ranging from
150ms to 1s after word onset. We use the resulting t and p-values as proxy to
quantify the performance of each model. These results are depicted in Figure
4 of the Supplementary Material. For concision purposes, we only report this metric averaged
between 150ms and 1s after word onset.

@@

Finally we investigate in Figure \ref{fig:megresult} whether B2B was sufficiently sensitive to reliably detect a multiplicity of subtle features, such as individual letters and part-of-speech. The vast majority the visual and lexical features appeared to be reliably detected (see Figure 3 in Supplementary Material). B2B thus promises to improve the detectability of subtle effects.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm, clip=True]{figures/meg_result.pdf}
  \caption{Cumulative estimates of word features as a function of time relative to word onset (chance level = 0). The dark blue area (word length) and dark red area (word frequency) correspond to the same data as those of the B2B average across subjects presented in \ref{fig:meg_twocurves}. A variety of visual features peak around 150ms, while a variety of lexical features tend to peak around 400ms.}
  \label{fig:megresult}
\end{figure}

### 2019-05-23 paper/paper.tex
almost done fellas

We perform two experiments to evaluate the performance of BB2R: one on controlled synthetic data, and a second one on a real, large-scale magneto-encephalography dataset.
%
We use scikit-learn to implement all of our simulations \citep{sklearn}.

>>>>

We perform two experiments to evaluate the performance of B2BR: one on controlled synthetic data, and a second one on a real, large-scale magneto-encephalography dataset.
%
We use scikit-learn to implement all of our simulations \citep{sklearn}.

### 2019-05-23 paper/supplementary.tex
almost done fellas

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm]{figures/pvalues_vertical.pdf}
  \caption{We show the average value and the standard deviation of the coefficients obtained with out method during the trials. the $\star$  symbol corresponds to statistically significant (t-test) nonzero values. We notice in particular that the letters q, x, y are under-represented, as expected. Similarly there were only few proper nouns (PROPN) in text corpora. }
  \label{fig:ridgebaselineresult}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm]{figures/pvalues_vertical.pdf}
  \caption{We show the average value and the standard deviation of the coefficients obtained with out method during the trials. the $\star$  symbol corresponds to statistically significant (t-test) nonzero values. We notice in particular that the letters q, x, y are under-represented, as expected. Similarly there were only few proper nouns (PROPN) in the word lists shown to subjects. }
  \label{fig:ridgebaselineresult}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\textwidth, trim=0cm 0cm 0cm 0cm]{figures/pvalues.pdf}
  \caption{We apply a statistical t-test to measure if coefficients were significantly different from the baseline value (at word onset, $t=0$ms).
  We compute the negative logarithm of the p-value (\textit{higher is better}: nonzero effects are more easily detected). We plot the average across features, over time.
  Full line: B2BR, dashed line: Forward regression. We see that our method more easily detects the influence of causes of MEG response.}
\end{figure}
